Probabilistic Programming

### 2014-04-21 paper/paper.tex
Add some discussion of model

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}

@@

Representation of programs in a markov model

@@

\begin{thebibliography}{1}

@@

@@

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}
\usepackage{listings}

\lstset{
	basicstyle=\footnotesize\ttfamily,
}

@@

\subsubsection{AST}

We work with programs at the level of abstract syntax tree (AST), using the
syntax tree format of Mozilla's Parser API \cite{parser api}. We use
esprima \cite{esprima}, an ECMAScript parser, to transform program source code into AST,
and escodegen \cite{escodegen} (ECMAScript code generator) to transform ASTs into program source
code.

\subsubsection{Model}

We encode the structure of an AST as a probabilistic model. The model is a data
structure that maps node paths to probability distributions of node types or
values. A node path is a list of node types and relationships that encodes the
unique position of a node in a program's AST. The probability distribution for a
node path is the set of possible node types or values that would appear in the
syntax tree following the given path, and the respective probabilities of their
occurance following the given path.

%\lstinputlisting[caption=Scheduler, style=json]{../rand.js}

@@

\clearpage
\begin{thebibliography}{1}

	\bibitem{esprima} Ariya Hidayat {\em Esprima}
		URL = \url{http://esprima.org/}

@@

	\bibitem{escodegen} Yusuke Suzuki {\em Escodegen}
		URL = \url{https://github.com/Constellation/escodegen}

	\bibitem{parser api} Mozilla Developer Network {\em SpiderMonkey Parser API}
		URL = \url{https://developer.mozilla.org/en-US/docs/SpiderMonkey/Parser_API}

@@

\clearpage
\section*{Appendix}

\begin{figure}[h!]
	\caption{model-sample.json}
	\centering
	A model generated from the program ``var x = 34"
\end{figure}

\lstinputlisting{model-sample.json}
